Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-12 manuscript/climate_sensitivity_draft.Rmd
update Rt by species
#100

Responses varied across species and by drought (Fig. **2**). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **~0.6**) and highest in *Fagus grandifolia* (mean $Rt$ = **~0.9**).

>>>>

Responses varied across species and by drought (Fig. **2**). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **0.66**) and highest in *Fagus grandifolia* (mean $Rt$ = **0.99**).
